---
title: "02_scrap_list_characters"
output:
  html_document: default
  html_notebook: default
---

Scrap and clean list of characters from https://en.wikipedia.org/wiki/List_of_Game_of_Thrones_characters

```{r eval=TRUE, warning=FALSE, message=FALSE}

library(httr)
library(tidytext)
library(knitr)
library(xml2)
library(rebus)
library(stringr)
library(rvest)
library(magrittr)
library(tidyverse)

```

```{r eval=TRUE, warning=FALSE, message=FALSE}

characters.dead <- readRDS("interim_output/characters.death.long.01.RDS") 

```

Download webpage

```{r eval=TRUE, warning=FALSE, message=FALSE}

characters <- read_html("https://en.wikipedia.org/wiki/List_of_Game_of_Thrones_characters")

characters %>% 
  write_xml("interim_output/characters_list.xml")

```

**Main characters**
```{r eval=TRUE, warning=FALSE, message=FALSE}

main.characters <- read_html("https://en.wikipedia.org/wiki/List_of_Game_of_Thrones_characters") %>% 
  xml_find_all("//table") %>%
  html_table(fill = T) %>%
  .[[5]] 

main.characters %<>% 
  .[2:nrow(main.characters),2] %>%
  str_replace_all(pattern = " \"" %R% ".*" %R% "\"", "" )

main.characters %>% sort()

```

**Side characters**
From second list (below), which descrives where characters were introduced.
```{r eval=TRUE, warning=FALSE, message=FALSE}

side.characters <- characters %>%
  rvest::html_nodes( ".column-width li") %>%
  html_text()

side.characters %<>% 
  str_match_all(pattern = "^.*" %R% " as" %R%  optional(one_or_more(rebus::or(".*", " "))) %R% capture(one_or_more(" [[:upper:]]" %R% WRD)) %R% optional(" ") %R% END) %>%
  map_chr(function(x){x[2]})
  
side.characters <- side.characters[!is.na(side.characters)]

side.characters <- c(side.characters, "Three-eyed Raven", "Aerys Targaryen")

side.characters %<>% sort()

side.characters

```


Some characters are 'young' versions of a main GoT character. We should delete those.

```{r eval=TRUE, warning=FALSE, message=FALSE}

side.characters.young <- side.characters %>% 
  str_subset(rebus::or("young", "child")) %>% 
  str_match(rebus::or("young ", "child ") %R% capture(".*")) %>%
  .[,2]
  
side.characters.young %>% unique

(side.characters.young %>% unique) %in% c(side.characters, main.characters)

```

Side characters from table
```{r eval=TRUE, warning=FALSE, message=FALSE}

side.characters.2 <- read_html("https://en.wikipedia.org/wiki/List_of_Game_of_Thrones_characters") %>% 
  xml_find_all("//table") %>%
  html_table(fill = T) %>%
  .[[6]] 

side.characters.2 <- side.characters.2[2:nrow(side.characters.2),2]

side.characters %<>% c(side.characters.2) %>% unique
  
```


```{r eval=TRUE, warning=FALSE, message=FALSE}

characters.all <- c(side.characters, main.characters, side.characters.young) %>% 
  unique() %>%
  sort

```

```{r eval=TRUE, warning=FALSE, message=FALSE}

characters.all.clean <- characters.all[c(-1,-2)] 

characters.all.clean <- characters.all.clean[!characters.all.clean %>%
  str_detect(pattern = rebus::or("young ", "child ") )] 

characters.all.clean %<>%
  str_replace(pattern = rebus::or("the ", "The ", "Maester ", "Grand Maester ", "Archmaester ") %R% optional(rebus::or("giant ", "second ")), replacement = "") %>%
  str_replace(pattern = rebus::or(" and various White Walkers", " of Vale"), replacement = ""   )

characters.all.clean <- characters.all.clean[characters.all.clean != "various White Walkers"]

characters.all.clean %>% sort()

```
```{r eval=TRUE, warning=FALSE, message=FALSE}

characters.all.clean %<>% c("Adrack Humble", "Axell Florent",  
                            "Barra", "Borba", "Dongo",
                      "Donnel Hill", "Gared", "Ghita", "Grey Wind",
                      "Griezhen mo Ullhor", "Guymon", "Harker", "Heward", "Catspaw assassin",
                      "Caleotte", "Cooper", "Hoster Tully", "Iggo", "Jack Bulwer",
                      "Jafer Flowers", "Joyeuse Erenford", "Kegs", "Khal Brozho",
                      "Khal Forzho", "Khal Qorro", "Khal Rhalko", "Kurleket",
                      "Leaf", "Lem Lemoncloak", "Lowell", "Eaton", "Mago",
                      "Mandon Moore", "Matthos Seaworth", "Mully", "Mycah",
                      "Olly's mother", "Oznak zo Pahl", "Ralf Kenning", "Ray",
                      "Rennick", "Robar Royce", "Sally", "Selyse Baratheon",
                      "Shaggydog", "Smitty", "Stiv", "Stonesnake",
                      "Summer", "Talisa Stark", "Tansy", "Tickler", "Tom",
                      "Torrhen Karstark", "Vardis Egen", "Varly", "Vayon Poole",
                      "Viserion", "Wallen", "Wendel Manderly", "White Rat", 
                      "Willem Lannister" , "Willis Wode", "Wyl", "Bobono", 
                      "Clarenzo", "Daisy", "Fennesz", "Gatins", "Belicho Paenymion",
                      "Lollys Stokeworth", "Marwyn", "Portan",
                      "Vance Corbray", "Razdal mo Eraz") 
      #in (these seem to be taken mostly from list of dead characters or from transcripts)

```



Clean list of dead characters
If a character does not appear in any episode and is just mentioned as dead, exclude it.
```{r eval=TRUE, warning=FALSE, message=FALSE}
#out
characters.dead %<>% 
  filter(!character %in% c("A white walker" , "Bannen", "Baratheon general",
                                              "Billy", "Despondent man", "Dornish guards", 
                                              "Drennan", "Frey soldiers", "Great master", "Jack",
                                              "Karstark lookout", "Lady", "Lady Cerwyn",
                                              "Lannister guard", "Medger's brother", "Medger Cerwyn",
                                              "Merchant captain", "Old man", "Old servant woman",
                                              "Othor" , "Rhaego", "Sally's father",
                                              "Son of the Harpy", "Stafford Lannister",
                                              "Thirteen", "Tortured prisoner", "Torturer",
                                              "Unnamed dwarf", "Unnamed man", "White Walker",
                                              "Zalla" ))

characters.dead %<>%
  mutate(character = character %>% 
           str_replace_all(pattern = rebus::or("Brother ", " and the villagers", "Maester ",
                                               "Master ", "Ser ", "The "), 
                           replacement = "") %>%
           str_replace(pattern = "Eddard Ned Stark", replacement = "Eddard Stark") %>%
         str_replace(pattern = "Jeor Morment", replacement = "Jeor Mormont") %>%
          str_replace(pattern = "Lord Petyr Baelish", replacement = "Petyr Baelish") %>%
          str_replace(pattern = "Ser Hugh", replacement = "Hugh")  %>%
          str_replace(pattern = "Blackfish", replacement = "Brynden Tully") %>%
          str_replace(pattern = "Thenn warg", replacement = "Thenn Warg") %>%
          str_replace(pattern = "Three-eyed raven", replacement = "Three-eyed Raven") %>%
          str_replace(pattern = "Walda Frey", replacement = "Walda Bolton")
         )

characters.dead %<>%  filter(!character %in% c("Thirteen","Torturer"))

(characters.dead$character[!characters.dead$character %in% characters.all.clean]) %>% sort

```


```{r eval=TRUE, warning=FALSE, message=FALSE}

characters.dead %>%
  count(season)

```


Export datasets 
```{r eval=TRUE, warning=FALSE, message=FALSE}

characters.dead %>% 
  write_rds("interim_output/characters.death.long.02.RDS")

characters.all.clean %>% 
  write_rds("interim_output/characters.all.02.RDS")

```
