---
title: "Scrap episode transcripts"
output: html_notebook
editor_options: 
  chunk_output_type: inline
---

Aim:
* Scrap and clean episode transcripts from genius.com;
* Relate all characters that were scrapped in script '02_scrap_characters_list.Rmd' to those in transcripts.

```{r eval=TRUE, warning=FALSE, message=FALSE}
rm(list = ls())

library(httr)
library(tidytext)
library(knitr)
library(xml2)
library(rebus)
library(stringr)
library(rvest)
library(magrittr)
library(tidyverse)

```


#Scrap list of GoT episodes
I manually limited it at 67
```{r eval=TRUE, warning=FALSE, message=FALSE}

if(!"episode_list_03.RDS" %in% list.files("interim_output/")){
  
episode.list <- read_html("https://en.wikipedia.org/wiki/List_of_Game_of_Thrones_episodes")

episode.list %<>%
  html_nodes( ".summary") %>%
  html_text() %>%
  str_replace_all(pattern = rebus::or("[[:punct:]]", "[[:cntrl:]]"),
                  replacement = "")

episode.list %>%
  write_rds("interim_output/episode_list_03.RDS")

}else{
  
episode.list <- read_rds("interim_output/episode_list_03.RDS")[1:67] 
  
}

```

# Scrap GoT transcripts from genius.com
There seem to be two different patterns in the links of genius.com
Ones end with 'script-annotated' and others just with 'annotated'.
e.g. "https://genius.com/Game-of-thrones-episode-annotated" and "https://genius.com/Game-of-thrones-episode-script-annotated"

## Create hypothetical links to transcript websites

```{r eval=TRUE, warning=FALSE, message=FALSE}

links.all.seasons.1 <- episode.list %>%
  tolower() %>%
  str_replace_all(pattern = " ", replacement = "-") %>%
  str_c("https://genius.com/Game-of-thrones", ., "annotated", sep = "-")

links.all.seasons.2 <- episode.list %>%
  tolower() %>%
  str_replace_all(pattern = " ", replacement = "-") %>%
  str_c("https://genius.com/Game-of-thrones", ., "script","annotated", sep = "-")

links.all.seasons.df <- data_frame(link_1 = links.all.seasons.1,
                                   link_2 = links.all.seasons.2)

```


## Check if links are valid 
Not all episodes are transcribed in genius.com webpage!
Spot missing transcribed episodes. Careful, this process requieres internet connextion and might take a few minutes.
_To update list of transcripts, delete the output of this chunk of code and run it_
```{r eval=TRUE, warning=FALSE, message=FALSE}

if(!"valid_transcript_links_03.RDS" %in% list.files("interim_output")){

valid.links.1 <- links.all.seasons.df$link_1 %>%
  map_lgl(url_success) 

valid.links.2 <- vector(mode = "logical", length = length(valid.links.1))

valid.links.2[valid.links.1 == F] <- links.all.seasons.df$link_2[valid.links.1 == F] %>%
  map_lgl(url_success)
  
links.all.seasons.df %<>%
  bind_cols(valid_links_1 = valid.links.1,
            valid_links_2 = valid.links.2)

valid.links <- if_else(links.all.seasons.df$valid_links_1 == T,
                       true = links.all.seasons.df$link_1,
                       false = if_else(links.all.seasons.df$valid_links_2 == T,
                                       true = links.all.seasons.df$link_2,
                                       false = "missing episode"))

valid.links %>%
  write_rds(path = "interim_output/valid_transcript_links_03.RDS")

}else{
  
  valid.links <- read_rds(path = "interim_output/valid_transcript_links_03.RDS")
  
}

```

**04-11-2017 There seem to be 22 episodes missing!** 
**Important: 2 episodes (22 and 23) have transcripts without names!**
```{r eval=TRUE, warning=FALSE, message=FALSE}

(valid.links == "missing episode") %>% sum()

valid.links

```

## Scrap transcripts
```{r eval=TRUE, warning=FALSE, message=FALSE}

season.vector <- c(str_c("season_", rep(1:6, 10)), rep("season_7", 7)) %>% sort

episode.number.vector <- c(rep(1:10, 6), rep(1:7))

episode.list.df <- data_frame(season = season.vector,
                              episode_number = episode.number.vector,
                              episode_name = episode.list,
                              link = valid.links)

episode.list.df

rm(valid.links, season.vector, episode.number.vector, links.all.seasons.1, links.all.seasons.2,
   links.all.seasons.df, episode.list)

```

## Convert trantscripts into tidy text
```{r eval=TRUE, warning=FALSE, message=FALSE}

if(!"all_transcripts_03.RDS" %in% list.files("interim_output/")){

all.transcripts <- episode.list.df$link[which(episode.list.df$link != "missing episode")] %>%
  map(function(x){read_html(x) %>%
  html_nodes(".lyrics p") %>%
  html_text })

 all.transcripts %>% 
   write_rds(path = "interim_output/all_transcripts_03.RDS")
 
}else{
  
  all.transcripts <- read_rds("interim_output/all_transcripts_03.RDS")
  
}
 
```


```{r eval=TRUE, warning=FALSE, message=FALSE}

all.transcripts %<>%
  map_chr(function(x){x %>% unlist %>% str_c(collapse = "_") })

episode.list.df$transcript <- NA

episode.list.df$transcript[episode.list.df$link != "missing episode"] <- all.transcripts


```


```{r eval=TRUE, warning=FALSE, message=FALSE}

rm(all.transcripts)

```

# Manually explore scrapped GoT transcripts
Transcripts can be manually explored here using the function writeLines. Careful with large outputs.
```{r eval=FALSE, warning=FALSE, message=FALSE}

episode.list.df$transcript[3] %>% 
  writeLines()

```

# Export objects
```{r eval=TRUE, warning=FALSE, message=FALSE}

episode.list.df %>%
  write_rds("interim_output/episode_list_transcripts_03.RDS")

```

