---
title: "04_Identify characters in transcripts"
output: html_notebook
editor_options: 
  chunk_output_type: inline
---

# Prepare session

```{r eval=TRUE, warning=FALSE, message=FALSE}

rm(list = ls())

library(stringr)
library(rebus)
library(magrittr)
library(tidyverse)

```

# Import data from previous scripts 

```{r eval=TRUE, warning=FALSE, message=FALSE}

episode.list.df <- read_rds("interim_output/episode_list_transcripts_03.RDS")

```


#Spot character names in transcripts
Transcriptions use names both in upper and lower case! 
e.g. 
* https://genius.com/Game-of-thrones-winter-is-coming-annotated
* https://genius.com/Game-of-thrones-the-kingsroad-annotated

There are some transcripts that use \ n pattern, others that don't

There are patterns of 'NAME (in valerian)' e.g:
'CERSEI (sighs): Thank you so much for your kind words'.

Names can have one or multiple words.


I think the following issues should be solved now:
TO DO: names can be preceeded by an interrogation mark in previous line. 
TO DO: this has to be changed to any character, including "-"

## Pattern to detect and extract character names 
```{r eval=TRUE, warning=FALSE, message=FALSE}

pattern.character.names <- rebus::or( rebus::or("[[:punct:]]","\\s","\n") %R% "[[:alpha:]]+" %R% rebus::one_or_more(" [[:alpha:]]+") %R% ":",
           rebus::or("[[:punct:]]","\\s","\n") %R% "[[:alpha:]]+" %R% rebus::zero_or_more(" [[:alpha:]]+") %R% " \\(" %R% rebus::one_or_more(rebus::or("[[:alpha:]]","\\s")) %R% "\\):")

```

**Export pattern to next script**
```{r eval=TRUE, warning=FALSE, message=FALSE}

pattern.character.names %>% 
  write_rds("interim_output/regex_pattern_identify_characters_transcripts.RDS")

```


## Apply pattern to obtain characters

** Main pattern**
```{r eval=TRUE, warning=FALSE, message=FALSE}

characters.transcripts.episode <- episode.list.df$transcript %>%
str_extract_all(pattern = pattern.character.names) %>%
  map(function(x) {x %>% str_replace_all(pattern = rebus::or(":", "\n", "\\.", 
"\\(" %R% rebus::one_or_more("[[:print:]]") %R% "\\)"), replacement = "")})
  
rm(pattern.character.names)

```


## Characters to upper
This is not the final list. Characters have to be cleaned in further scripts.
```{r eval=FALSE, warning=FALSE, message=FALSE}

characters.transcripts.episode %>%
  unique()

```

```{r eval=TRUE, warning=FALSE, message=FALSE}

characters.transcripts.episode %<>%
map(function(x){
toupper(x) %>% 
str_replace_all("[[:punct:]]", "") %>%
str_trim(side = "both") } )

```

Character counts by episode
```{r eval=TRUE, warning=FALSE, message=FALSE}

characters.transcripts.count <- characters.transcripts.episode %>%
  map(function(x) {x %>% table %>% sort(decreasing = T)})
  
characters.transcripts.count

```

```{r eval=TRUE, warning=FALSE, message=FALSE}

characters.transcripts.count %>%
  map(function(x){x %>% rownames %>% str_count(pattern = rebus::exactly("AEMON")) %>% sum() })


```


All characters
```{r eval=TRUE, warning=FALSE, message=FALSE}

characters.transcripts <- characters.transcripts.episode %>% 
  unlist %>%
  unique %>%
  sort

```


## Export matched characters

Export object with all characters
```{r eval=TRUE, warning=FALSE, message=FALSE}

characters.transcripts %>%
  write_rds("interim_output/characters_matched_transcripts.04.RDS")

```


Export object with character counts by episode
```{r eval=TRUE, warning=FALSE, message=FALSE}

characters.transcripts.count %>%
  write_rds("interim_output/characters_matched_transcripts_count_by_episode.04.RDS")

```


