---
title: "17_plot_cumulative_counts_of_appearances"
output: html_notebook
editor_options: 
  chunk_output_type: inline
---

```{r}

rm(list = ls())

library(RColorBrewer)
library(stringr)
library(ggplot2)
library(magrittr)
library(tidyverse)

options(scipen = 9999)

```

# Import data

## Non-imputed relative transcript appearances data
```{r}

char_estimated_alive_cumulative_counts_wide <- 
  read_rds("counts/alive/estimated_clean_alive_cumulative_proportions_wide_by_episode_11.RDS")

```

## Imputed relative transcript appearances data




## Summaries of IMDB cast appearances by character

This includes sum of counts, sum of counts by season and mean number of transcript appearances per imdb cast appearance.
```{r eval=TRUE, warning=FALSE, message=FALSE}

char_counts_imdb_summary <- read_rds("interim_output/imdb_summary_counts/imdb_counts_and_means_10.RDS")

```

## List of missing episodes
```{r eval=TRUE, warning=FALSE, message=FALSE}

episode_list_df <- readRDS("interim_output/episode_list_transcripts_03.RDS")

episode_list_df

```


# Compute non-imputed dataset to plot relative appearances
Ideally, and especially for a plot, appearances in each episode should sum to 1

To do The graph should:
__MAIN__
* show some comparison between dead and alive characters


__SECONDARY__


## Labels x scale for the plot
```{r}

labels_x_scale <- char_estimated_alive_cumulative_counts_wide %>%
  names() %>% str_subset(pattern = "^s\\d{2}e\\d{2}$")

names_labels_x_scale <- labels_x_scale %>% 
  str_extract(pattern = "^s\\d{2}e01$") 

names_labels_x_scale <- if_else(!is.na(names_labels_x_scale),
                                true = names_labels_x_scale,
                                false = "")

names(labels_x_scale) <- names_labels_x_scale

```



## Pick 'top n' characters with highest proportion of appearances at any time 

I need to compute this from imputed counts.

To do: it's curious what the cutoff_cast_appearances for top 20 indicates. Are seasons 6 and 7 more disperse in terms of _cast_ appearances?
```{r}

top_number <- 15

#seasons <- char_counts_imdb_summary %>%
 # ungroup %>%
  #select(ends_with("_sum_imdb_cast")) %>%
  #names()

## first x episodes can be excluded to avoid inserting characters which are not really main characters.

excluded_first_episodes <- c("s01e01", "s01e02", "s01e03")


## this table shows the maximum proportion each character achieved (in terms of estimated cumulative proportions)
char_max_proportion_cumulative_counts <- char_estimated_alive_cumulative_counts_wide %>%
  gather(key = "episode", value = "proportion", matches(match = "^s\\d{2}e\\d{2}$")) %>%
   filter(!episode %in% excluded_first_episodes) %>%
  group_by(character.names.wikipedia, identifier) %>%
  summarise(max_proportion = max(proportion, na.rm = T)) %>%
  arrange(desc(max_proportion)) 
 
# identifiers of characters arranged according to 
char_estimated_alive_cumulative_counts_arranged_id <- char_max_proportion_cumulative_counts %$%
  identifier
 
selected_characters_graph_df <- data_frame(identifier = char_estimated_alive_cumulative_counts_arranged_id,
                                           row_ =  1:length(char_estimated_alive_cumulative_counts_arranged_id))
  
char_estimated_alive_cumulative_counts_wide_for_plot <- char_estimated_alive_cumulative_counts_wide %>%
  left_join(selected_characters_graph_df, by = "identifier") %>%
  arrange(row_)

rm(selected_characters_graph, excluded_first_episodes)

```




## Delete missing episodes

```{r}

vector_missing_episodes <- (episode_list_df$link == "missing episode") 

char_estimated_alive_cumulative_counts_wide_for_plot[,which(vector_missing_episodes)+2] <- NA

qual_col_pals <- brewer.pal.info[brewer.pal.info$category == 'qual',]
col_vector <- unlist(mapply(brewer.pal, qual_col_pals$maxcolors, rownames(qual_col_pals)))

  ## delete from labels as well

labels_x_scale <- labels_x_scale[!vector_missing_episodes]

```



# Plot cumulative counts (for alive characters only)
```{r}

top_char_estimated_alive_cumulative_counts_wide <- char_estimated_alive_cumulative_counts_wide_for_plot %>%
  head(top_number)
  
p_1 <- top_char_estimated_alive_cumulative_counts_wide %>%
  gather(key = "season_episode", value = "prop", starts_with("s") ) %>%
  mutate(prop = prop * 100) %>%
  filter(!is.na(prop)) %>%
  ggplot(aes(x = factor(season_episode), y = prop, group = as_factor(character.names.wikipedia), col = as_factor(character.names.wikipedia) )) +
  ggplot2::geom_line(size = 2) +
  scale_color_manual(values=col_vector) +
  scale_x_discrete(labels = labels_x_scale %>% names) +
  labs(x = "Episode", y = "% appearances", col = "Character")

p_1 %>% 
  write_rds("output_articles/static_shiny_graph_16.rds")

p_1

```

To do: I probably need to explore most transcript appearances 'in any given season' for those seasons where we have good data. The cool part would be to plot both alive and dead characters.

Prepare graph data so I have to do less steps in Shiny app.
```{r}

char_estimated_alive_cumulative_counts_wide_for_shiny <- char_estimated_alive_cumulative_counts_wide_for_plot %>%
  gather(key = "season_episode", value = "prop", starts_with("s") ) %>%
  mutate(proportion = prop * 100) %>% 
  filter(!is.na(proportion)) %>% #these NAs are imputed NAs. This is because in the 'alive' appearances I imputed NAs after death of character. 
  ungroup %>%
  mutate(episode = factor(season_episode),
         character = as_factor(character.names.wikipedia)) %>%
  select(-season_episode, -character.names.wikipedia)

# cut to a max of 100 chars

char_estimated_alive_cumulative_counts_wide_for_shiny %<>%
  filter(row_ <= 100)

```



# Export auxiliary tools for Shiny app
```{r}

if(!"interim_output/shiny_app" %in% list.dirs("interim_output")){
  
  dir.create("interim_output/shiny_app")
  
}

export_for_shiny <- list(char_counts = char_estimated_alive_cumulative_counts_wide_for_plot,
                         labels_x_scale = labels_x_scale,
                         col_vector = col_vector,
                         vector_missing_episodes = vector_missing_episodes,
                         plot_data = char_estimated_alive_cumulative_counts_wide_for_shiny) 

export_for_shiny %>%
  write_rds("interim_output/shiny_app/export_for_shiny_17.rds")

```


